SMT-Based Context-Bounded Model Checking for Embedded Systems: State of the Art and Future Trends

### 2016-03-22 paper.tex
review 2.1 Induction-based Verification of C Programs

One possible way to achieve completeness in BMC techniques is to prove that an invariant (assertion) is \textit{k}-inductive~\cite{EenS03,Sheera00}. The main challenge of such approach relies on computing and strengthening inductive invariants from the program. In particular, loop invariants computed from the program must be inductive (and not just invariant) for the corresponding verification conditions to be valid~\cite{Bradley07}. As a consequence, even if \textit{k}-induction procedures successfully compute such assertions, which are indeed invariant, those must be inductive so that verifiers can automatically prove program correctness.

There are several invariant generation algorithms that discover linear and polynomial relations among integer and real variables, in order to provide loop invariants and also to discover the memory ``shape'' in programming languages with pointers~\cite{pips:2013,Henry:2012}. The current literature also reports successful applications of \textit{k}-induction based verification algorithms for hardware and software systems using invariants generation and strengthening, mostly based on interval analysis. In particular, Gadelha {\it et al.}, Beyer {\it et al.}, and Brain {\it et al.} presented new verification algorithms for proving correctness of (a large set of) C programs, by mathematical induction, in a completely automatic way ({\it i.e.}, users do not need to provide the loop invariant)~\cite{Gadelha15,Beyer15,Brain15,Rocha15}.

Additionally, \textit{k}-induction based verification was also applied to ensure that (restricted) C programs (1) do not contain violations related to data races~\cite{Donaldson10,Kinductor} considering the  Cell BE processor and (2) do respect time constraints, which are specified during the system design phase~\cite{EenS03}. The \textit{k}-induction algorithm is also a well-established technique in hardware verification, where it is easily applied, due to the monolithic transition relation present in such designs~\cite{EenS03,Sheera00,GrosseLD09}.

However, there is still little evidence, in the available literature, that model checking hardware and software systems, using \textit{k}-induction (and invariants), can be efficiently exploited in embedded system verification. That happens due to the distinctive characteristics mentioned earlier, which influence the embedded system development and also the employed verification processes. Additionally, there is still a lack of studies for embedded software verifiers to exploit the combination of different invariant generation algorithms, including analysis to discover linear inequalities, polynomial equalities and inequalities, and invariants about memory and variable aliasing~\cite{Bradley07}.

>>>>

One promising approach to achieve completeness in BMC techniques is to prove that an invariant (assertion) is \textit{k}-inductive~\cite{EenS03,Sheera00}. The main challenge, however, of such approach relies on computing and strengthening inductive invariants from the program. In particular, loop invariants computed from the program must be inductive (and not just invariant) for the corresponding verification conditions to be valid~\cite{Bradley07}. As a consequence, even if \textit{k}-induction procedures successfully compute such assertions, which are indeed invariant, those must be inductive so that verifiers can automatically prove program correctness.

There are several invariant generation algorithms that discover linear and polynomial relations among integer and real variables, in order to provide loop invariants and also to discover the memory ``shape'' in programming languages with pointers~\cite{pips:2013,Henry:2012}. The current literature also reports successful applications of \textit{k}-induction based verification algorithms for hardware and software systems using invariants generation and strengthening, mostly based on interval analysis.

Gadelha {\it et al.}, Beyer {\it et al.}, and Brain {\it et al.} presented new verification algorithms for proving correctness of (a large set of) C programs, by mathematical induction, in a completely automatic way ({\it i.e.}, users do not need to provide the loop invariant)~\cite{Gadelha15,Beyer15,Brain15,Rocha15}. Additionally, \textit{k}-induction based verification was also applied to ensure that (restricted) C programs (1) do not contain violations related to data races~\cite{Donaldson10,Kinductor} considering the  Cell BE processor and (2) do respect time constraints, which are specified during the system design phase~\cite{EenS03}. The \textit{k}-induction algorithm is also a well-established technique in hardware verification, where it is easily applied, due to the monolithic transition relation present in such designs~\cite{EenS03,Sheera00,GrosseLD09}.

However, there is still little evidence, in the available literature, that model checking hardware and software systems, using \textit{k}-induction (and invariants), can be efficiently exploited in embedded system verification. That happens due to the distinctive characteristics mentioned earlier, which influence the embedded system development and also the employed verification processes. Additionally, there is still a lack of studies for embedded software verifiers to exploit the combination of different invariant generation and strengthening algorithms, including analysis to discover linear inequalities, polynomial equalities and inequalities, and invariants about memory and variable aliasing~\cite{Bradley07}.
